The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-01-26 article/article.tex
add fibonacci and golden ration
classes of placement algorithms

\section{Multiple-choice balls-into-bins}
\label{sec:multiple-choice}
The \emph{single-choice balls-into-bins strategy} (Section \ref{sec:single-choice}) chooses one bin for each ball. A \emph{multiple-choice balls-into-bins strategy} generalizes this idea by choosing $d$ bins and placing the ball into the least full bin.

\todo{discuss the 3 classes}

@@

>>>>

\section{Multiple-choice balls-into-bins}
\label{sec:multiple-choice}
The \emph{single-choice balls-into-bins strategy} (Section \ref{sec:single-choice}) chooses one bin uniformly and independently at random for each ball. A \emph{multiple-choice balls-into-bins strategy} generalizes this idea by  choosing $d \geq 2$ bins and placing the ball into the least full bin. Depending on how the $d$ locations are sampled, we distinguish three classes of placement algorithms \cite{VOC03}.

Thus, let $B$ be the set of bins $\{1,2...n\}$, $\Omega = B^{d}$ be the sample space and $\mathcal{F} = 2^{\Omega}$ be the set of measurable events. We are only interested in events that represent a set of bins of size $d$. Thus, let $\mathcal{F}_d = \{\mathcal{E} \in \mathcal{F}: \left\vert \mathcal{E} \right\vert = d\}$ and set $\Pr\left(\mathcal{E}  \right) = 0$  $\forall \mathcal{E} \in \mathcal{F} \setminus \mathcal{F}_d $. The three classes of algorithms are distinguished by the probability function $\Pr\left(\mathcal{E}\right)$ for events $\mathcal{E}_d \in \mathcal{F}_d$:
\begin{itemize}
\item \emph{Uniform and independent.} Choose each of the $d$ bins for a ball uniformly and independently at random from the set of bins $B$. This implies 
\[
\forall \mathcal{E} \in \mathcal{F}_d: \Pr\left(\mathcal{E}\right) = \frac{1}{n ^{d}}
\]
\item \emph{Non-uniform and independent.} Choose the $i$th bin from $B$ independently at random according to some probability function
\[
\Pr: B \rightarrow \left[0,1\right]
\]

\item \emph{Non-uniform and dependent.} Choose the $d$ bins for a ball from $\Omega$ at random:
\[
\Pr: B^{d} \rightarrow \left[0,1\right]
\]

\end{itemize}

@@

\subsection{Analysis}
\label{sec:analysis}

\subsubsection{Preliminaries}
\label{sec:preliminaries}
\todo{where to put this? required for  bound of always-go-left in intro}
We define $d$-ary Fibonacci numbers as follows. For $k \leq0$, $F_d(k) = 0$, $F_d(1) = 1$ and for $k \geq 1$,

\[
F_d(k) = \sum_{i=1}^{d}F_d(k-i)
\]
Furthermore, define 
\[
\Phi_d = \lim_{k \rightarrow \infty} \sqrt[k]{F_d(k)}
\]
Notice that $F_2$ corresponds to the usual Fibonacci numbers, while $\Phi_2 $ corresponds to the golden ratio \cite{Knuth73}, which is generalized to $\Phi_d$, for which 
\[
i, j \in \mathbb{N}, i < j \Rightarrow \Phi_i < \Phi_j
\]
and 
\[
\lim_{d\rightarrow \infty} \Phi_d = 2
\]
hold.
